### 2019-05-25 doc/chapters/using_bitcoins.tex
fixed use of old code

The relevant parts for the property to be verified are the following two lines.
\begin{lstlisting}
  val prevOutputs = transaction.inputs.map(_.previousOutput)
  val noDuplicateInputs = prevOutputs.distinct.size == prevOutputs.size
\end{lstlisting}
It gathers all inputs output.
On this previous outputs it calls distinct and checks if the size stays the same.
Distinct removes duplicates, so if there was two times the same input the size of inputs before calling distinct would be greater.

>>>>

The relevant parts for the property to be verified are the following two lines.
\begin{lstlisting}
  val prevOutputTxIds = transaction.inputs.map(_.previousOutput.txId)
  val noDuplicateInputs = prevOutputTxIds.distinct.size == prevOutputTxIds.size
\end{lstlisting}
It gathers all inputs output transaction ids.
On this previous outputs ids it calls distinct and checks if the size stays the same.
Distinct removes duplicates, so if there was two times the same input transaction id the size of those ids would be greater before calling distinct.

There is a bug in those two lines, as described in the next chapter.
